Bayesian Detection of Bias in Peremptory Challenges Using Historical Strike Data

### 2022-11-17 analysis/paper_draft3.Rmd
sentence edit

To evaluate the proposed method, we conducted a simulation study using Stan `r rstan::stan_version()`, a Hamiltonian Monte Carlo engine for Bayesian inference by way of `r R.version$version.string` and RStan [@rstan]. <!--To measure convergence, we used trace plots, the Gelman-Rubin convergence diagnostic and Geweke’s diagnostics [@Gelman1992;@Gelman1998;@Geweke1992].--> These simulations primarily show how much our ability to detect bias was affected the size of the historical data and by how much the power prior discounted the weight of the historical data. As introduced above, $b > 0$ represents a prosecutor's bias against a prospective juror within the cognizable class, while $b = 0$ denotes no bias. For simplicity, we assume the defense attorney has no bias.

>>>>

To evaluate the proposed method, we conducted a simulation study using Stan `r rstan::stan_version()`, a Hamiltonian Monte Carlo engine for Bayesian inference by way of `r R.version$version.string` and RStan [@rstan]. <!--To measure convergence, we used trace plots, the Gelman-Rubin convergence diagnostic and Geweke’s diagnostics [@Gelman1992;@Gelman1998;@Geweke1992].--> These simulations primarily show how much the size of the historical data affects our ability to detect bias and how much the power prior discounted the weight of the historical data. As introduced above, $b > 0$ represents a prosecutor's bias against a prospective juror within the cognizable class, while $b = 0$ denotes no bias. For simplicity, we assume the defense attorney has no bias.
